\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[left=0.8in,top=0.4in,right=0.8in,bottom=0.5in]{geometry}
\renewcommand{\baselinestretch}{1.4}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{6pt}{3pt}
\setlist[itemize]{leftmargin=*, topsep=1pt, itemsep=0pt, parsep=0pt}

\hypersetup{
  colorlinks=true,
  urlcolor=blue,
  linkcolor=blue
}

\title{\textbf{Zhengze (Z) Zhou}\vspace{-3em}}
\author{}
\date{}

\begin{document}

\pagestyle{empty}
\maketitle

%% ── Contact ──────────────────────────────────────────────────────────────────
\begin{center}
  \small
  \href{mailto:zz433@cornell.edu}{\underline{zz433@cornell.edu}}
  $|$ +1 (607) 319-6302
  $|$ \href{https://zhengzezhou.github.io}{\underline{zhengzezhou.github.io}}
  $|$ \href{https://scholar.google.com/citations?user=MEEbBwMAAAAJ&hl=en}{\underline{Google Scholar}}
  $|$ \href{https://www.linkedin.com/in/z-zhou-42139bb7/}{\underline{LinkedIn}}
\end{center}

\vspace{1mm}

%% ── About ────────────────────────────────────────────────────────────────────
\section*{About}

I am currently a Staff AI Engineer at LinkedIn Core AI, based in New York. Previously, I was
a Research Scientist at Meta, where I worked on large-scale recommendation systems and search ranking.
I received my PhD in Statistics from Cornell University under the supervision of Giles Hooker.
My current research focus is on LLM post-training (distillation and reinforcement learning),
inference efficiency, and generative recommendations.

%% ── Professional Experience ──────────────────────────────────────────────────
\section*{Professional Experience}

\noindent\textbf{Staff AI Engineer} \hfill June 2025 -- Present \\
LinkedIn Core AI, New York, NY

\begin{itemize}
  \item Led post-training optimization for LinkedIn hiring agents via supervised fine-tuning and reinforcement learning.
  \item Developed LLM serving efficiency via prompt compression using reinforcement learning,
        achieving a 10$\times$ reduction in prompt length with significant cost and latency savings.
  \item Architected generative recommendation models for LinkedIn's core user surfaces
        (Feed, Ads), driving next-generation user engagement at scale.
  \item Published research work on semantic search and LLM post-training.
\end{itemize}

\vspace{1mm}

\noindent\textbf{Research Scientist} \hfill June 2021 -- June 2025 \\
Meta, New York, NY

\begin{itemize}
  \item Tech lead for content search ranking, overseeing the full ML pipeline from
        training data and model architecture to online A/B evaluation.
  \item Pioneered LLM integration for search relevance evaluation, improving assessment
        efficiency and quality at scale.
  \item Led the first generative recommendation system launch for Instagram Reels,
        significantly enhancing user experience and engagement.
  \item Drove deployment of a foundational user interest model to personalize
        Instagram Reels recommendations at scale.
\end{itemize}

\vspace{1mm}

\noindent\textbf{Software Engineer (Machine Learning) Intern} \hfill May -- August 2020 \\
\noindent Meta (Facebook), Menlo Park, CA

\noindent\textbf{Applied Scientist Intern} \hfill May -- August 2019 \\
\noindent Amazon.com, Inc., Seattle, WA

\noindent\textbf{Applied Scientist Intern} \hfill May -- August 2018 \\
\noindent Amazon.com, Inc. (A9.com), Palo Alto, CA

%% ── Education ────────────────────────────────────────────────────────────────
\section*{Education}

\noindent\textbf{PhD}, Statistics, Cornell University \hfill 2021 \\
Advisor: Prof. Giles Hooker. Thesis: \textit{Statistical Inference for Machine Learning:
Feature Importance, Uncertainty Quantification and Interpretation Stability.}

\vspace{1mm}

\noindent\textbf{MS}, Computer Science, Cornell University \hfill 2020

\vspace{1mm}

\noindent\textbf{BS}, Statistics and Probability, Peking University \hfill 2016

%% ── Publications ─────────────────────────────────────────────────────────────
\section*{Selected Publications}

\noindent\textit{Preprints}

\vspace{1mm}

\noindent 1. Yuanda Xu, Hejian Sang, \textbf{Zhengze Zhou}, Ran He, Zhipeng Wang,
\textit{PACED: Distillation at the Frontier of Student Competence}, arXiv:2603.11178, 2026.

\noindent 2. Hejian Sang, Yuanda Xu, \textbf{Zhengze Zhou}, Ran He, Zhipeng Wang,
\textit{Not All Tokens Are Needed (NAT): Token Efficient Reinforcement Learning}, arXiv:2603.06619, 2026.

\noindent 3. Hejian Sang, Yuanda Xu, \textbf{Zhengze Zhou}, Ran He, Zhipeng Wang, Jiachen Sun,
\textit{On-Policy Self-Distillation for Reasoning Compression}, arXiv:2603.05433, 2026.

\noindent 4. Yuanda Xu, Hejian Sang, \textbf{Zhengze Zhou}, Ran He, Zhipeng Wang,
\textit{Overconfident Errors Need Stronger Correction: Asymmetric Confidence Penalties
for Reinforcement Learning}, arXiv:2602.21420, 2026.

\noindent 5. Fedor Borisyuk, Sriram Vasudevan, \ldots, \textbf{Zhengze Zhou}, et al.,
\textit{Semantic Search At LinkedIn}, arXiv:2602.07309, 2026.

\vspace{2mm}

\noindent\textit{Refereed Publications}

\vspace{1mm}

\noindent 6. Kayhan Behdin, Qingquan Song, \textbf{Zhengze Zhou}, et al.,
\textit{Scaling Up Efficient Small Language Models Serving and Deployment for Semantic Job Search},
\textbf{MLSys 2026} (to appear).

\noindent 7. Yichen Zhou, \textbf{Zhengze Zhou} and Giles Hooker,
\textit{Approximation Trees: Statistical Reproducibility in Model Distillation},
Data Mining and Knowledge Discovery, 38(5):3308--3346, 2024.

\noindent 8. Xiaojian Zhang, \textbf{Zhengze Zhou}, Yiming Xu and Xilei Zhao,
\textit{Analyzing Spatial Heterogeneity of Ridesourcing Usage Determinants
Using Explainable Machine Learning},
Journal of Transport Geography, 114:103782, 2024.

\noindent 9. \textbf{Zhengze Zhou}, Giles Hooker and Fei Wang,
\textit{S-LIME: Stabilized-LIME for Model Explanation},
\textbf{KDD 2021}, pp.\ 2429--2438.

\noindent 10. \textbf{Zhengze Zhou} and Giles Hooker,
\textit{Unbiased Measurement of Feature Importance in Tree-Based Methods},
ACM Transactions on Knowledge Discovery from Data (TKDD), 15(2):1--21, 2021.

\noindent 11. \textbf{Zhengze Zhou}, Lucas Mentch and Giles Hooker,
\textit{V-Statistics and Variance Estimation},
Journal of Machine Learning Research (JMLR), 22(287):1--48, 2021.

\noindent 12. Richard B. Darlington and \textbf{Zhengze Zhou},
\textit{SILR: A New Exact Test for Demonstrating That an Effect Exists in Binary Trials},
OSF Preprints, 2021.

\noindent 13. Xilei Zhao, \textbf{Zhengze Zhou}, Xiang Yan and Pascal Van Hentenryck,
\textit{Distilling Black-Box Travel Mode Choice Model for Behavioral Interpretation},
arXiv:1910.13930, 2019.

%% ── Academic Service ─────────────────────────────────────────────────────────
\section*{Academic Service}

\begin{itemize}
  \item Reviewer: ICLR 2022, 2023, 2024; ICML 2022; NeurIPS 2021; AAAI 2024
  \item Reviewer: Annals of Statistics; Journal of the American Statistical Association;
        Machine Learning (Springer)
\end{itemize}

%% ── Honors and Awards ────────────────────────────────────────────────────────
\section*{Honors and Awards}

\begin{itemize}
  \item 1st Place, 2018 Citadel Datathon @ Cornell
  \item Outstanding Graduate Award, Peking University, 2016
  \item May 4th Scholarship, Peking University, 2015
\end{itemize}

\end{document}
